Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-12-14 paper/main.tex
Added distribution of file sizes hashed when downloading

\section{Measurements of Tahoe data}
\label{sec:results:tahoedata}

% TODO: Fiks denne tabellen så den ikke overflower
% TODO: Sleng inn samme for download
Table \ref{tbl:tahoe:datauploaded} and describes the distribution of the
different input sizes of data that Tahoe-\ac{LAFS} sends to the hash function
when uploading and downloading the test vectors. E.g. to upload the 100 1-byte
files, 15700 hashes had to be calculated, and about 64\% of these were of size
106 byte.

@@

\section{Measurements of Tahoe operations}

The sum of the amount of time it took for the underlying hash library to
calculate the hash operations are exhibited in Figures \ref{fig:graph:1001b},
\ref{fig:graph:1001kb}, \ref{fig:graph:501mb}, \ref{fig:graph:5100mb} and
\ref{fig:graph:11gb}. We call this \emph{Time spent hashing}.

>>>>

\section{Measurements of Tahoe data}
\label{sec:results:tahoedata}
% TODO: Update text and Captions to better describe what is going on.

Tables \ref{tbl:tahoe:datauploaded} and \ref{tbl:tahoe:datadownloaded} and
describes the distribution of the different input sizes of data that
Tahoe-\ac{LAFS} sends to the hash function when uploading and downloading the
test vectors. E.g. to upload the 100 1-byte files, 15700 hashes had to be
calculated, and about 64\% of these were of size 106 byte.

@@

\section{Measurements of Tahoe operations}
The sum of the amount of time it took for the underlying hash library to
calculate the hash operations are exhibited in Figures \ref{fig:graph:1001b},
\ref{fig:graph:1001kb}, \ref{fig:graph:501mb}, \ref{fig:graph:5100mb} and
\ref{fig:graph:11gb}. We call this \emph{Time spent hashing}.
